% original author: Jeremy Kun
\documentclass[11pt]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage{color}

% title metadata
\firstname{Kristina}
\familyname{Tropf}
\title{} 
\email{kristina.tropf@gmail.com}

\definecolor{MidnightBlue}{rgb}{0.5, .1, .35}

\begin{document}
\maketitle
\section{Experience}
	\cventry{Feb. 2017 - Present}
			{Operations Supervisor}
			{The Juice Standard}
			{Las Vegas}{NV}
			{Prepare and serve cold-pressed juices, nut milks, fruit smoothies, and healthy snacks. Deliver exceptional customer service, provide free juice samples, and act as a subject matter expert on the company's products. Complete various managerial duties such as handling cash drawers, ensuring sanitation standards, and opening/closing the store.}
	\cventry{Aug. 2016 - Present}
			{Certified Temporary Tutor}
			{Silvestri Junior High School}
			{Las Vegas}{NV}
			{Worked with students both individually and in small groups to provide tutoring and guidance. Kept accurate records on student progress, administered tests, and implemented strategies to improve general reading comprehension and math/science proficiency.}
	\cventry{July 2017 - Apr. 2018}
			{Barista}
			{Starbucks}
			{Las Vegas}{NV}
			{Prepared and served food and beverages, operated a cash register, performed support tasks like cleaning and restocking, and provided customers with quality service and an unforgettable Starbucks experience.}
	\cventry{Aug. 2016 - June 2017}
			{Cashier/Food Prep}
			{Sambalatte Torrefazione Cafe}
			{Las Vegas}{NV}
			{Provided  exceptional face-to-face  customer service, assisted customers with drink orders, regularly restocked products, and helped maintain store operations.}
	\cventry{Oct. 2015 - Present}
			{Substitute Teacher}
			{Clark County School District}
			{Las Vegas}{NV}
			{Substituted primarily English for grades 6th to 8th. Frequently requested by multiple teachers at Silverstri Junior High School, Schofield Middle School, and Levitt Middle School.}
	\cventry{Sep. 2015 - Oct. 2015}
			{Apprentice Secondary English Teacher}
			{CCSD Alternative Route to Licensure Program (ARL)}
			{Las Vegas}{NV}
			{Completed online and in-person instructional sessions, along with classroom-based training and mentoring with an experienced 12th grade English teacher.}
	\cventry{Aug. 2014 - Aug. 2015}
			{Middle School English Teacher}
			{Lake Mead Christian Academy}
			{Las Vegas}{NV}
			{Taught 6th, 7th, and 8th grade English at a local private school. Prepared and administered assignments and tests, created and implemented lesson plans, and assisted with the day-to-day operation of the school.}
	\cventry{Oct. 2011 - Aug. 2014}
			{TLC (Quality Assurance)/Live Chat Representative}
			{Zappos.com}
			{Las Vegas}{NV}
			{Started in the call center answering phones. Promoted to TLC, a specialty team within the call center with the purpose of upholding quality standards by evaluating customer phone calls, creating training presentations, relaying information to employees, and providing one-on-one customer service training. Rotated to the Live Chat team to further assist customers and to train employees on the Live Chat system and Bourbon email client.}
\section{Education}
	\cventry{2005 - 2009}
			{Dual B.A. in Business Management and Biblical Studies}
			{Rochester College}
			{Rochester Hills}{MI}
			{Relevant courses include Labor Relations, Operations Management, Small Business and Enterpanuership, Financial Plan and Control Systems, Leadership Theory, Organizational Behavior, Principals of Management, and Human Resources Management.}
\section{Skills}
	\cvline{Customer Service}{9 years of customer service experience in multiple channels, including face-to-face, phone, email, and live chat.}
	\cvline{Computer Skills}{Consistent typing speed of 60+ WPM. Skilled with Google Apps and Microsoft Office.}
	\cvline{Teaching and Training}{2 years of classroom teaching experience with CCSD both as a Substitute and CTT. Trained Zappos employees in the live chat and email customer service tools.}
	\cvline{Quality Assurance}{Skilled in evaluating customer service phone calls and live chats to ensure that quality standards are being met.}
\end{document}